### 2016-08-17 latex/paper.tex
Indent equations for clarity

The elongation produces a net force on the rim parallel to the original spoke axis equal to
\begin{equation}\label{eq:sF1}
f_1 = \left(\frac{E_sA_s\Delta l}{l}\hat{\bm{n}}_1\right) = \frac{E_sA_s}{l} \hat{\bm{n}}_1 \cdot \bm{u}_n 
\end{equation}
The rotation of the spoke produces net forces on the rim perpendicular to the original spoke axis due to the rotation of the initial tension vector.
\begin{equation}\label{eq:sF2}
f_2 = T \sin{\Omega_1} \approx \frac{T}{l} \hat{\bm{n}}_2 \cdot \bm{u}_n
\end{equation}
\begin{equation}\label{eq:sF3}
f_3 = T \sin{\Omega_2} \approx \frac{T}{l} \hat{\bm{n}}_3 \cdot \bm{u}_n
\end{equation}
since $\hat{\bm{n}}_1,\hat{\bm{n}}_2,\hat{\bm{n}}_3$ are mutually orthogonal, the total force on the rim is given by $\bm{f} = \bm{k}_f \cdot \bm{u}_n$, where the spoke stiffness matrix is given by
\begin{equation}\label{eq:kf}
\bm{k}_f = \frac{E_sA_s}{l}\hat{\bm{n}}_1\hat{\bm{n}}_1 + \frac{T}{l}(\hat{\bm{n}}_2\hat{\bm{n}}_2 + \hat{\bm{n}}_3\hat{\bm{n}}_3)
\end{equation}
The first term in Eqn.~\ref{eq:kf} is the {\bf elastic stiffness} and the second term is the {\bf tension stiffness}. The tension stiffness is the component responsible for the transverse vibrations of a guitar string, e.g.

Following the approach of Smith~\cite{Smith1901a} and Pippard~\cite{Pippard1932d}, we will approximate the spoke system as a continuum which exerts a distributed load on the rim. The stiffness per unit length is defined by the sum of the spoke stiffnesses in one periodic grouping of spokes, divided by the arc length of the grouping.
\begin{equation}\label{eq:kbar}
\bar{\bm{k}} = \frac{1}{2\pi R}\left(\frac{n_s}{n_p}\right) \sum_i^{n_p} \bm{k}_{f, i}
\end{equation}
The distributed load $\bar{\bm{f}}$ does an amount of work per unit length equal to
\begin{equation}\label{eq:w_spokes}
\bar{w} = \int_0^{u_n} \bar{\bm{f}} \cdot d\bm{u}_n = \frac{1}{2} \bm{u}_n \cdot \bar{\bm{k}} \cdot \bm{u}_n
\end{equation}
The line of action is assumed to pass sufficiently close to the rim shear center that any difference between the displacement of the spoke nipple and the displacement of the shear center can be ignored. The total strain energy stored in the spoke system is equal to
\begin{equation}\label{eq:Us}
U_{spokes} = \int_0^{2\pi} \bar{w} \, ds = \frac{1}{2}\left( \bar{k}_{uu}u^2 + \bar{k}_{vv}v^2 + \bar{k}_{ww}w^2 + 2\bar{k}_{uv}uv + 2\bar{k}_{uw}uw + 2\bar{k}_{vw}vw\right)
\end{equation}

>>>>

The elongation produces a net force on the rim parallel to the original spoke axis equal to
	\begin{equation}\label{eq:sF1}
	f_1 = E_sA_s\left(\frac{\Delta l}{l}\right)\hat{\bm{n}}_1 = \frac{E_sA_s}{l} \hat{\bm{n}}_1 \cdot \bm{u}_n 
	\end{equation}
The rotation of the spoke produces net forces on the rim perpendicular to the original spoke axis due to the rotation of the initial tension vector.
	\begin{equation}\label{eq:sF2}
	f_2 = T \sin{\Omega_1} \approx \frac{T}{l} \hat{\bm{n}}_2 \cdot \bm{u}_n
	\end{equation}
	\begin{equation}\label{eq:sF3}
	f_3 = T \sin{\Omega_2} \approx \frac{T}{l} \hat{\bm{n}}_3 \cdot \bm{u}_n
	\end{equation}
since $\hat{\bm{n}}_1,\hat{\bm{n}}_2,\hat{\bm{n}}_3$ are mutually orthogonal, the total force on the rim is given by $\bm{f} = \bm{k}_f \cdot \bm{u}_n$, where the spoke stiffness matrix is given by
	\begin{equation}\label{eq:kf}
	\bm{k}_f = \frac{E_sA_s}{l}\hat{\bm{n}}_1\hat{\bm{n}}_1 + \frac{T}{l}(\hat{\bm{n}}_2\hat{\bm{n}}_2 + \hat{\bm{n}}_3\hat{\bm{n}}_3)
	\end{equation}
The first term in Eqn.~\ref{eq:kf} is the {\bf elastic stiffness} and the second term is the {\bf tension stiffness}. The tension stiffness is the component responsible for the transverse vibrations of a guitar string, e.g.

Following the approach of Smith~\cite{Smith1901a} and Pippard~\cite{Pippard1932d}, we will approximate the spoke system as a continuum which exerts a distributed load on the rim. The stiffness per unit length is defined by the sum of the spoke stiffnesses in one periodic grouping of spokes, divided by the arc length of the grouping.
	\begin{equation}\label{eq:kbar}
	\bar{\bm{k}} = \frac{1}{2\pi R}\left(\frac{n_s}{n_p}\right) \sum_i^{n_p} \bm{k}_{f, i}
	\end{equation}
	The distributed load $\bar{\bm{f}}$ does an amount of work per unit length equal to
	\begin{equation}\label{eq:w_spokes}
	\bar{w} = \int_0^{u_n} \bar{\bm{f}} \cdot d\bm{u}_n = \frac{1}{2} \bm{u}_n \cdot \bar{\bm{k}} \cdot \bm{u}_n
	\end{equation}
The line of action is assumed to pass sufficiently close to the rim shear center that any difference between the displacement of the spoke nipple and the displacement of the shear center can be ignored. Therefore $\bm{u}_n = \bm{u}$. Substituting a lateral buckling displacement $\bm{u}=u\hat{\bm{e}}_1$ into Eqn. \ref{eq:w_spokes} and integrating over the length of the rim gives the strain energy stored in the spoke system.
	\begin{equation}\label{eq:Us}
	U_{spokes} = \int_0^{2\pi} \bar{w} \, ds = \frac{1}{2} \bar{k}_{uu}u^2
	\end{equation}
